Modeling memory and taxis to analyze migrations

### 2021-06-14 text/ms.Rmd
,,,
Updates ... notably, new migration indices

@@

@@

@@

>>>>

## Migration

Under what conditions is migration stable:

sigma_t, sigma_x, 
epsilon, alpha, 
beta, lambda, 
x_peak = 30, t_peak = 25

@@

*Under what conditions can we adapt.*>

@@

*Under what conditions can be learn.*

@@

However, the ability to migrate was highly dependent on the nature of the resource dynamics.  In particular, the reinforcement of memory and foraging is strongest when patches are concentrated in time, but relatively large in space.  **ALSO SOME STUFF WE LEARN ABOUT THE INTERACTION BETWEEN DIFFUSION, RESOURCE FOLLOWING, SOCIALITY**

It is worth considering the assumptions of our model with respect to a biological population.  Notably, the fact that the memory is not easily interpreted as an

**Describing conditions for adaptability.**

**Describing conditions for learning migration.**

**Describing conditions for climate change resilience.**
